Parallel Simulation of Adaptive Random Boolean Networks

### 2016-07-14 Paper/paper.tex
Knuth algo: references

	\paragraph{Knuth algorithm.} The algorithm is based on the following observation: $\mathbf{S}(\tau) = \mathbf{S}(2\tau)$ if and only if $\tau$ is a multiple of an attractor length $\mu$, i. e. $\tau = n\mu$. In order to find $\tau$, two copies of a Boolean network are launched, one copy performs one state update per iteration, and the other one performes two. Then the states $\mathbf{S}(t)$ and $\mathbf{S}(2t)$ are compared, and $\tau$ is considered found if they are equal. To apply ADRR, one needs to know nodes' mean state on an attractor. It can be found without determining the value of $\mu$. First, one should find sum of nodes' states on $t \in (\tau, 2\tau]$ by calulating a state sum vector $\Sigma(t) = \Sigma(t - 1) + \mathbf{S}(2t) + \mathbf{S}(2t + 1) - \mathbf{S}(t)$ on each iteration. After $\tau$ is found, mean state of the $i$-th node on the attractor is $\langle\sigma_i\rangle = \Sigma_i(\tau) / \tau$. Having found $\tau$ it is possible to obtain the length of the attractor by finding $\mu$ such that $\mathbf{S}(\tau) = \mathbf{S}(\tau + \mu)$.

>>>>

	\paragraph{Knuth algorithm \cite{knuth1981art}.} The algorithm is based on the following observation: $\mathbf{S}(\tau) = \mathbf{S}(2\tau)$ if and only if $\tau$ is a multiple of an attractor length $\mu$, i. e. $\tau = n\mu$. In order to find $\tau$, two copies of a Boolean network are launched, one copy performs one state update per iteration, and the other one performes two. Then the states $\mathbf{S}(t)$ and $\mathbf{S}(2t)$ are compared, and $\tau$ is considered found if they are equal. To apply ADRR, one needs to know nodes' mean state on an attractor. It can be found without determining the value of $\mu$. First, one should find sum of nodes' states on $t \in (\tau, 2\tau]$ by calulating a state sum vector $\Sigma(t) = \Sigma(t - 1) + \mathbf{S}(2t) + \mathbf{S}(2t + 1) - \mathbf{S}(t)$ on each iteration. After $\tau$ is found, mean state of the $i$-th node on the attractor is $\langle\sigma_i\rangle = \Sigma_i(\tau) / \tau$. Having found $\tau$ it is possible to obtain the length of the attractor by finding $\mu$ such that $\mathbf{S}(\tau) = \mathbf{S}(\tau + \mu)$. For more detailed description of this algorithm with application to RBNs see \cite{bhattacharjya1996median}.
